Numerical Investigation of Viscous Flow Instabilities in Heterogeneous Porous Media

### 2017-12-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

%%%%%%%%%%%% 
\subsection{Initial Model Validation}\label{section:results_validation}
Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrate the model capability to capture viscous crossflow in immiscible displacement in heterogeneous porous media. The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is $4$ $\times$ $2$ unit-length and fully saturated with fluid 2 ({\it VR}=1). Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$. Boundary conditions also include no-flux across upper and lower borders. The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a). The spatial discontinuities of permeability distribution will create a rough pressure field, \ie the pressure gradient is discontinuous across the interface between different permeability zones thus the flow will be lead to the high permeability region. This will cause difficulties for numerically solving fluid flows in heterogeneous porous media.

\medskip
Numerical simulation was performed in modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10. Initial and boundary conditions remain the same, and flow behaviour qualitatively agree validated against laboratory experiments conducted by \citet{evans_1994}. Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1. They also show the development of wetting phase through the four subdomains, demonstrating the preferential flow path through high-permeability regions. Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}.

>>>>

%%%%%%%%%%%% 
\subsection{Initial Model Validation}\label{section:results_validation}
Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrate the model capability to capture viscous crossflow in immiscible displacement in heterogeneous porous media. The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is $4$ $\times$ $2$ unit-length and fully saturated with fluid 2 ({\it VR}=1). Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$. Boundary conditions also include no-flux across upper and lower borders. The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a). The spatial discontinuities of permeability distribution will create a rough pressure field, \ie the pressure gradient is discontinuous across the interface between different permeability zones thus the flow will be lead to the high permeability region. \green{PS: I AM NOT SURE WHICH INFO YOU WANT TO CONVEY IN THIS SENTENCE ... ACTUALLY THIS IS NOT CORRECT AS THERE IS NO DISCONTINUITY IN EITHER PERMEABILITY (AS INFERRED B4) OR IN PRESSURE, JUST A LARGE K AND P DISTRO ...} \red{IS THERE ANY COMMENT WRT FIG 4b-c AT VR=1?}

\medskip
Numerical simulation was performed in modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10. Initial and boundary conditions remain the same, and flow behaviour qualitatively agree validated against laboratory experiments conducted by \citet{evans_1994}. Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1. They also show the development of wetting phase through the four subdomains, demonstrating the preferential flow path through high-permeability regions. Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}. \red{KOSTAS ... COULD YOU REVIEW THIS SECTION ... IT INITIALLY REFERS TO VR=1 AND THEN TO VR=10 ... BUT IT IS NOT CLEAR IF THE PLOTS IN FIG 4 REFER TO VR1 OR VR10 ...}
